|

### 2022-08-16 manuscript_BE/manuscript_BE.Rmd
Edits in the source code to be able to sit some fish with FAA and others with PAA

```{r post, fig.cap='Posterior distributions for parameter values $\\gamma$ and $\\eta$ for the three models (Full model, chaining only and penalty only). We show the kernel density estimates, below the mode (black dot) and the 66 (light blue shade) and 95\\% (grey shade)  highest posterior density interval for the two parameters. On the top, panels a and b show posterior distributions for a full model, including chaining ($\\gamma$) and penalty ($\\eta$). Panel c, shows the $\\gamma$ estimate from model with only chaining. Panel d shows the $\\eta$ estimate from a model with only penalty. Panel e, shows a measure of fit for all models, namely the distribution of pseudo-$R^2$ obtained from sampling the posterior distribution of parameter values.',out.width='100%',fig.height=6,cache=FALSE}

>>>>

```{r post, fig.cap='Posterior distributions for parameter values $\\gamma$ and $\\eta$ for the six models, three for each type of agent (Agents: FAA and PAA; models: Full model, chaining only and penalty only). We show the kernel density estimates, below the mode (black dot) and the 66 (light color shade) and 95\\% (grey shade)  highest posterior density interval for the two parameters. Colors blue and red denote agents FAA and PAA respectively. On the top, panels a and b show posterior distributions for a full model, including chaining ($\\gamma$) and penalty ($\\eta$). Panel c, shows the $\\gamma$ estimate from model with only chaining. Panel d shows the $\\eta$ estimate from a model with only penalty. Panel e, shows a measure of fit for all models, namely the distribution of pseudo-$R^2$ obtained from sampling the posterior distribution of parameter values.',out.width='100%',fig.height=6,cache=FALSE}
